Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-02-05 parallel-tractability-J-v9/evaluation.tex
added the experiments of lubm and yago

\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{\text{prc}}$}

In this part, we evaluate the implemented prototype system ParallelDHL
for DHL$(\circ)$ materialization based on
Algorithm~$\mathsf{A}_{\text{prc}}$. We also provide evaluation
results for the state-of-the-art reasoning system RDFox
\cite{MotikNPHO14}, which can also handle parallel ontology
materialization. Since RDFox is already a mature system, developed by
several people over several years, we only provide the results for
reference, as a direct comparison with our initial, not yet optimized
prototype is not possible.

\textbf{Datasets}.
We select eight ontologies from the data sources given in the previous subsection;
four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
the rest of them does not satisfy the simple-concept or the simple-role
restriction.
The chosen eight ontologies are real ontologies and are applied in different fields.
The basic information for these ontologies
is summarized in Table~\ref{tab:info}.

\begin{table}[htb]
\centering
\caption{Information about the test ontologies, where
  $|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring
  in the ontology, $|\mathcal{A}|$ denotes the number of assertions
  in the ABox and the last column states whether the
  ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$}
\begin{tabular}{>{\hspace*{5mm}}ccrrc<{\hspace*{5mm}}}
\hline
\textbf{Ontology Name} & \textbf{Field} &
                                          $|\mathcal{T}|+|\mathcal{R}|$
  & $|\mathcal{A}|$ & $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
\hline

Finance&finance&1,934&6,152&no\\

Molecule&chemistry&43&0&no\\

GrossAnatomy&anatomy&2,276&13&no\\

Skeleton&medicine&815&0&no\\

\hline

ChemistryPrimitive&chemistry&167&0& yes\\

FacebookOnto&social networking&185&28& yes\\

Mahabharata&literature&69&2,036& yes\\

Transportation&traffic&925&511& yes\\

\hline
\end{tabular}
\label{tab:info}
\end{table}

In order to compare ABoxes of a similar scale, we generate a limited
number of ABox assertions with respect to the TBoxes and RBoxes for
the test ontologies using the generation method proposed by
\citet{Elhaik98}.  For each test ontology, e.g., the Finance ontology,
we generate 5 new ontologies with different ABoxes, denoted
Finance-$i$ ($i\in\{1,2,3,4,5\}$). The index $i$ indicates that the
number of ABox assertions of Finance-$i$ is $i\times100,000$. We also
use the term ``Finance series" to denote the five generated ontologies
for the Finance ontology. The other test ontologies are processed
similarly.

\begin{table}[htb]
\centering
\caption{Analysis of the reasoning results, where the \emph{minimal time
  ratio} is the minimal reasoning time
of ParallelDHL divided by the minimal reasoning time of RDFox and the
\emph{average speedup} is $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
 where $T_i$ is the reasoning time with $i$ threads allocated}
{\setlength{\tabcolsep}{6mm}
\begin{tabular}{crrrrr}
\hline
series & 1 & 2 & 3 & 4 & 5\\
\hline
\multicolumn{6}{c}{minimal time ratio}\\%[-1mm]
% \multicolumn{6}{c}{{\footnotesize minimal reasoning time
% of ParallelDHL/minimal reasoning time of RDFox}}\\
\hline
Finance&0.54&1.36&0.94&0.99&1.70\\
Molecule&0.94&0.79&0.96&0.98&1.07\\
GrossAnatomy&0.65&0.48&0.84&0.77&0.83\\
Skeleton&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
ChemistryPrimitive&1.29&1.54&1.68&1.14&0.93\\
FacebookOnto&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
Mahabharata&1.19&1.19&0.99&0.84&0.89\\
Transportation&0.24&0.52&0.51&0.65&0.49\\
\hline
\multicolumn{6}{c}{average speedup of ParallelDHL with increasing
  number of threads}\\%[-1mm]
% \multicolumn{6}{c}{{\footnotesize
%   $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
%  where $T_i$ is the reasoning time with $i$ threads allocated}}\\
\hline
Finance&3.06&1.88&2.29&2.95&2.73\\
Molecule&1.04&1.24&1.13&1.07&1.05\\
GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
Skeleton&3.28&1.84&1.65&1.74&1.96\\
ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
\hline
\multicolumn{6}{c}{average speedup of RDFox with increasing
  number of threads}\\%[-1mm]
% \multicolumn{6}{c}{{\footnotesize
%   $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
%  where $T_i$ is the reasoning time with $i$ threads allocated}}\\
\hline
Finance&1.01&1.04&1.13&1.11&1.19\\
Molecule&0.90&1.03&0.95&1.01&0.99\\
GrossAnatomy&0.87&0.99&0.94&0.96&0.98\\
Skeleton&1.13&1.01&1.06&1.08&1.08\\
ChemistryPrimitive&1.28&1.16&1.14&1.11&1.15\\
FacebookOnto&1.22&1.08&1.07&1.09&1.09\\
Mahabharata&1.24&1.07&1.13&1.10&1.12\\
Transportation&1.14&1.04&1.03&1.08&1.11\\
\hline
\end{tabular}
% \begin{tabular}{crrrrr}
% \hline
% series & 1 & 2 & 3 & 4 & 5\\
% \hline
% &0.54&1.36&0.94&0.99&1.70\\
% Finance&3.06&1.88&2.29&2.95&2.73\\
% &1.01&1.04&1.13&1.11&1.19\\
% \hline
% &0.94&0.79&0.96&0.98&1.07\\
% Molecule&1.04&1.24&1.13&1.07&1.05\\
% &0.90&1.03&0.95&1.01&0.99\\
% \hline
% &0.65&0.48&0.84&0.77&0.83\\
% GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
% &0.87&0.99&0.94&0.96&0.98\\
% \hline
% &1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
% Skeleton&3.28&1.84&1.65&1.74&1.96\\
% &1.13&1.01&1.06&1.08&1.08\\
% \hline
% &1.29&1.54&1.68&1.14&0.93\\
% ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
% &1.28&1.16&1.14&1.11&1.15\\
% \hline
% &\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
% FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
% &1.22&1.08&1.07&1.09&1.09\\
% \hline
% &1.19&1.19&0.99&0.84&0.89\\
% Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
% &1.24&1.07&1.13&1.10&1.12\\
% \hline
% &0.24&0.52&0.51&0.65&0.49\\
% Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
% &1.14&1.04&1.03&1.08&1.11\\
% \hline
% \end{tabular}
}
\label{tab:expresult}
\end{table}

\textbf{The Experimental Results}.
We evaluated ParallelDHL and RDFox over the above eight ontology series.
The running environment is a DELL server with a
memory of 16 GiB and 4 cores.
For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads, respectively)
for ParallelDHL and RDFox in each experiment. The resulting reasoning
times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
where the abscissa of each line graph records the numbers of ABox assertions,
the ordinate records the reasoning times (in milliseconds),
and each of the five curves in different colors denotes the trend of reasoning time with the
corresponding number of threads allocated (we use line-$k$ to denote the curve
corresponding to $k$ threads).

% We further process the collected data and fill the results in Table~\ref{tab:expresult}, where each cell corresponds
% to a test ontology (see the row label) and a newly generated ABox (distinguished by the column labels);
% the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
% of ParallelDHL divided by the minimal reasoning time of RDFox;
% (2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
% the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
% (3) \emph{the average speedup of RDFox}.
% The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
% The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
% Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
% threads allocated.
% In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~\ref{tab:expresult}.

We further process the collected data and fill the results in Table~\ref{tab:expresult}, where each cell corresponds
to a test ontology (see the row label) and a newly generated ABox
(distinguished by the series column labels).
The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
The indicator `speedup' and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
threads allocated.
In the following, we give a detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~\ref{tab:expresult}.

\textbf{Analysis of the Experimental Results}.
According to the theoretical results in Section~\ref{sec:ptonto},
materialization of the
ontologies not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
(Finance, Molecule, GrossAnatomy and Skeleton)
may not be tractable in parallel. In other words,
parallel techniques may not work for improving the efficiency of materialization.
This is shown in the line graphs of Figure~\ref{fig:linegraph}.
We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
that do not belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
intersect to some degree. This is more obvious in the line graphs for
the Finance and GrossAnatomy
series. For example, in line graph $lg1$,
line-2 stays higher than line-6, but lower than line-4.
The intersection of lines indicates that reasoning time cannot
obviously be reduced with more threads allocated.
This is also supported by the results of the average speedups.
From Table~\ref{tab:expresult}, we can see that the average speedups of ParallelDHL and RDFox
for the ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
are more stable compared with the other ones, i.e., with an average of
$1.4$ for ParallelDHL. This means that the reasoning time can be reduced on average
by $1.4$ times with two more threads allocated
for ParallelDHL, and, $1.1$ for RDFox. For the four ontology series
that do not belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$,
the average speedups have a higher volatility. For example,
the Finance and Skeleton series lead to high average speedups that reach up to $3$,
while, for the Molecule and GrossAnatomy series, the average speedups are even below $1$.
In summary, from the experiments on the test ontology series,
parallelism leads to a more effective improvement for materializing the ontology series
that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared
with the ones outside of this fragment.

By analyzing the experimental results of ParallelDHL and RDFox, we have that
ParallelDHL is competitive system despite not yet being highly optimized.
From Table~\ref{tab:expresult}, we can find that most of the minimal time ratios are close to $1$.
This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
In particular, for the GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
only requires one fifth of the minimal reasoning time of RDFox.
On the other hand, for most ontology series,
the average speedups of ParallelDHL are overall higher than that of RDFox.
The main difference between ParallelDHL and RDFox lies in that ParallelDHL applies
the optimizations designed for Algorithm~$\mathsf{A}_{\text{opt}}$ (see Section~\ref{sec:ptclass}).
The higher average speedups of ParallelDHL also verifies the validity of the optimizations
used in Algorithm~$\mathsf{A}_{\text{opt}}$.
One may note that ParallelDHL is on average 3 times slower than RDFox
when handling the Skeleton series.
The main reason is that the computation of the \texttt{rch} relations
requires a large amount of time and the situation of path twisting occurs in Skeleton series.
This makes the the optimization based on \texttt{rch} relations invalid as discussed
in Section~\ref{sec:ptonto}. {\color{red}What does the bold font in
  the table mean?}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
\label{fig:linegraph}
\end{center}
\end{figure}

\begin{figure}[htbp]
  \centering
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{experimentalResults/1-Finance-simple}
    \subcaption{Finance (lg1)\label{fig:financepdhl}}
  \end{minipage}
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{experimentalResults/2-molecule-simple}
    \subcaption{Molecule (lg3)\label{fig:moleculepdhl}}
  \end{minipage}\\
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-simple}
    \subcaption{GrossAnatomy (lg5)\label{fig:grossanatomypdhl}}
  \end{minipage}
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-simple}
    \subcaption{Skeleton (lg7)\label{fig:skeletonpdhl}}
  \end{minipage}
  \caption{Materialization time in ms for ParallelDHL for the
    ontologies that do not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.~\label{fig:eval}}
\end{figure}

\begin{figure}[htbp]
  \centering
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{experimentalResults/1-Finance-rdfox}
    \subcaption{Finance (lg2)\label{fig:financerdfox}}
  \end{minipage}
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{experimentalResults/2-molecule-rdfox}
    \subcaption{Molecule (lg4)\label{fig:moleculerdfox}}
  \end{minipage}\\
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-rdfox}
    \subcaption{GrossAnatomy (lg6)\label{fig:grossanatomyrdfox}}
  \end{minipage}
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-rdfox}
    \subcaption{Skeleton (lg8)\label{fig:skeletonrdfox}}
  \end{minipage}
  \caption{Materialization time in ms for RDFox for the
    ontologies that do not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.~\label{fig:eval}}
\end{figure}

>>>>

\begin{table}
\centering
\caption{The statistics of the test ontologies}
\begin{tabular}{|l|r|r|r|r|r|}
\hline
ontology&$\sharp$concept&$\sharp$role&$\sharp$individual&$\sharp$axiom$^{a}$&$\sharp$assertion\\
\hline
lubm-50&48&32&1,082,818&99&11,601,923\\
lubm-100&48&32&2,179,766&99&23,837,579\\
lubm-150&48&32&3,243,523&99&35,466,709\\
lubm-200&48&32&4,341,309&99&46,537,764\\
lubm-250&48&32&5,421,894&99&58,125,155\\
yago-core&65,318&74&4,077,882&55,615&45,277,896\\
\hline
\multicolumn{5}{l}{$^{a}$ \small the number of TBox and RBox axioms.}\\
\end{tabular}
\label{tab:onto}
\end{table}

\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}

We implement a prototype system ParallelDHL for DHL$(\circ)$ materialization
based on Algorithm~$\mathsf{A}_{prc}$. Since ParallelDHL is evaluated in the
platform which has the limited memory space and the fixed number of processors,
the parallel assumption given in Section~\ref{sec:alg-bsc} does not apply to ParallelDHL.
In the implementation of ParallelDHL, we use a hash function to map any rule instance
to the identifier of some processor. Thus, when performing ParallelDHL,
each processor handles a group of rule instances.

We run ParallelDHL on LUBM and YAGO to further analyze these
two kinds of ontologies. We also use the reasoning system, RDFox \cite{MotikNPHO14},
for comparison. We use five LUBM ontologies, lubm-50, lubm-100, lubm-150, lubm-200
and lubm-250, where lubm-50 contains the descriptions of 50 universities (the other ontologies
are explained similarly). For YAGO, we use its core version, denoted by yago-core.\footnote{
The yago-core ontology is available at https://www.mpi-inf.mpg.de/departments/databases-and-information-systems/research/yago-naga/yago/downloads/.}
The yago-core ontology is a subset of the full YAGO dataset. It does not include the datatype statements, the links
between different data sources, the degrees of confidence and other kinds of
annotations that we do not consider in this work. The statistics of the above ontologies is given in Table~\ref{tab:onto}.
The running platform for this experiment is a server with a 50 Gigabyte RAM and 8 physical cores, in each core
three logic threads can be allocated.

We run the LUBM ontologies and the yago-core ontology on RDFox and ParallelDHL with different numbers of
threads (respectively 1,4,8,16 and 24).
The reasoning times are collected in Table~\ref{tab:result}. We also give Figure~\ref{fig:reasoningtime} to
clearly compare the two systems.
In Figure~\ref{fig:reasoningtime}(left), the abscissa records the five LUBM ontologies,
the ordinate records the reasoning times with 24 threads being allocated;
In Figure~\ref{fig:reasoningtime}(right), the abscissa records the reciprocal of the number of threads, and
the ordinate records the reasoning times over the yago-core ontology.

\begin{table}
\centering
\caption{The reasoning-time results (seconds)}
\begin{tabular}{|l|r|r|r|r|r|r|r|}
\hline
&\small$\sharp$thread&lubm-50&lubm-100&lubm-150&lubm-200&lubm-250&yago-core\\
\hline
\multirow{5}{*}{ \textbf{RDFox}}&1&23.01&42.8&71.92&88.64&111.96&105.73\\
                    &4&5.97&11.64&18.5&22.31&25.59&35.5\\
                    &8&4.88&5.89&9.95&11.21&12.8&19.07\\
                    &16&3.18&3.75&8.37&9.16&12.19&13.22\\
                    &24&1.92&3.9&6.21&7.74&9.58&11.81\\
\hline
\multirow{5}{*}{ \small{\textbf{ParallelDHL}}}&1&93.66&213.75&376.39&498.34&693.49&773.06\\
                    &4&21.71&54.03&111.2&123.76&159.82&223.4\\
                    &8&9.44&23.04&55.78&67.29&86.41&98.33\\
                    &16&4.02&12.7&20.9&35.63&43.91&47.08\\
                    &24&4.06&9.82&16.84&22.31&27.47&34.48\\
\hline
\end{tabular}
\label{tab:result}
\end{table}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{fig-reasoningtime.eps}
\caption{(left) the reasoning times over LUBM ontologies; (right) the reasoning times over yago-core.}
\label{fig:reasoningtime}
\end{center}
\end{figure}

From Table~\ref{tab:result}, we can see that for lubm-50 these two systems perform equally well.
For the other ontologies, ParallelDHL is comparable to RDFox with several threads being allocated.
For lubm-250 and yago-core, ParallelDHL delays obviously when only one thread is allocated.
The reason is that the computation of the relation $S_{\textit{\!\tiny rch}}$ occupies a large amount of time. When
more threads are allocated, ParallelDHL has a better efficiency.
Although ParallelDHL is not such optimized as RDFox, it also shows the scalability.
From the two line graphs in Figure~\ref{fig:reasoningtime},
we can see a linear trend of the reasoning times of both RDFox and ParallelDHL.
This also indicates that ParallelDHL will finish the materialization tasks on the test ontologies
in a shorter period of time with more threads being allocated.

\subsection{The Discussion of The Depths of Materialization Graphs}

From the complexity analysis for Algorithm~$\mathsf{A}_{bsc}$, we have that the computing time of
Algorithm~$\mathsf{A}_{bsc}$ depends on the number of iterations of \ref{alg1:updateG},
which equals to the depth of the constructed materialization graph (see the proof of Theorem~\ref{theorem:a1}).
Thus, the depth of the target materialization graph determines the computing time of
Algorithm~$\mathsf{A}_{bsc}$. This conclusion also applies to Algorithm~$\mathsf{A}_{opt}$
based on the analysis in Section~\ref{sec:opt}. In this part,
we discuss the influence of the depths of the materialization graphs
for the test ontologies.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{fig-graphdepth.eps}
\caption{The statistics of the materialization graphs of lubm-250 (left) and yago-core (right).}
\label{fig:graphdepth}
\end{center}
\end{figure}

For the five test LUBM ontologies and the yago-core ontology, we record the total depth
of the materialization graph for each ontology and the number of nodes in different depths.
We have that all of the LUBM ontologies have the depth of 6 for their
materialization graphs, while the materialization graph of the yago-core ontology
has the depth of 9.
We use the histograms to graphically display the detailed data of lubm-250 and yago-core in Figure~\ref{fig:graphdepth},
where for each of the two histograms
the abscissa records the depths from the bottom of a materialization graph to the top,
the histograms denote the amount of nodes in each depth.

From the above results, we can find that the graph depths are far less than
the sizes of the input ontologies. Since the graph depth determines the computing
time of Algorithm~$\mathsf{A}_{bsc}$ and Algorithm~$\mathsf{A}_{opt}$ as discussed
at the beginning of this part,
the test ontologies should be materialized efficiently using these two algorithms.
The obvious difference of the reasoning times of the test ontologies is due to the limited memory space and the fixed number
of processors and the inapplicability of the parallel assumption given in Section~\ref{sec:alg-bsc}.
This results in that the computing
time of ParallelDHL does not depend only on the number of iterations of \ref{alg4:updateG}
of Algorithm~$\mathsf{A}_{prc}$ as analyzed in Section~\ref{sec:practicalAlg}.
It depends on several factors: the balancing of workload, the delay of some processors,
the I/O blocking, etc. Since these issues are not our focus, we do not analyze them in this work.
On the other hand, the results of the graph depths
indicate that we can improve the performance of the materialization task by using more
memory space and more processors.
